---
name: Alexis
surname: Polidoro
position: "MA Candidate - Geography"
address: "
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4"
phone: +1 905 525 9140
www: straightupnorth.ca/alexis-polidoro/
email: "polidora@mcmaster.ca"

date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
---
```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show = "asis", 
                      # Width of figures in output document is 60% of linewidth
                      out.width = "0.6\\linewidth", 
                      fig.align = "center")
```

```{r current-year}
# Retrieve current year
current_year <- as.numeric(as.character(Sys.time(), '%Y')) # Update year
```

```{r load-packages}
library(dplyr) # Data carpentry
library(ggplot2) # Grammar of graphics
library(here) # Package to simplify finding files within projects
library(readr) # Package to read external data, e.g., csv files
library(scholar) # Package to analyze citation data from Google Scholar
library(tibble) # Package to work with simple data frames
library(vitae) # Templates and functions to simplify the production and maintenance of curriculum vitae.
```

# About me

* Master of Arts Candidate from McMaster University with a specialization in Arctic Geography and community engagement. I have over five years’ experience as a student within the school of Earth, Environment, and Society at McMaster University, where I have also worked as a teaching assistant, research assistant, and McPherson Institute student partner. Currently, I am collaborating on a federally funded project with team members across Canada to investigate how well research is serving Nunavummiut (the people of Nunavut). 
<!--


# Education

```{r education-details}
# Read assets and pass to detailed_entries()
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   # Inputs will be parsed as LaTeX code when .protect=FALSE
                   .protect = FALSE)
```


# Employment History

```{r employment-details}
# Read assets and pass to detailed_entries()
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

#Talks

##Conference Presentations

```{r conference-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  # Filter honors of type "Conference"
  dplyr::filter(What == "Conference") %>% 
  detailed_entries(what = Title, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

##Panels

```{r panel-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  # Filter honors of type "Panel"
  dplyr::filter(What == "Panel") %>% 
  detailed_entries(what = Title, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```
##Other Speaking Events

```{r other-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  # Filter honors of type "Other"
  dplyr::filter(What == "Other") %>% 
  detailed_entries(what = Title, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

# Honours

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  # Filter honors of type "Scholarship"
  dplyr::filter(Type == "Scholarship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  # Filter honors of type "Scientific Awards"
  dplyr::filter(Type == "Scientific Awards") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

# Publications
## Reports

```{r refereed-publications}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) %>%
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```
